Process Flux Data

### 2021-06-24 R/01-process-flux.Rmd
update processing rmd, remove old r scripts, update makefile with new rmd

fluxes <-
  nested %>% 
  mutate(tidy = map(model, tidy)) %>% 
  unnest(tidy) %>% 
  filter(term == 'days') %>% 
  group_by(flux_date) %>% 
  arrange(estimate, .by_group = TRUE) %>% 
  select(-data, -model, -term) %>% 
  ungroup() %>% 
  mutate(passage = as.numeric(flux_date)) %>% 
  mutate(estimate_rank = rank(estimate)) %>% 
  filter(passage != 6) %>% 
  select(-std.error, -statistic, -p.value)

fluxes$estimate_log10 <- log10(fluxes$estimate + abs(min(fluxes$estimate)) + 0.001)

# Identify the selected jars in the fluxes dataframe
selected$selected <- TRUE
fluxes <- left_join(fluxes, selected, by = c('passage', 'jar'))
fluxes$selected <- !is.na(fluxes$selected)
```

>>>>

fluxes <-
  nested %>% 
  mutate(tidy = map(model, tidy)) %>% 
  unnest(tidy) %>% 
  filter(term == 'days') %>% 
  group_by(flux_date) %>% 
  arrange(estimate, .by_group = TRUE) %>% 
  select(-data, -model, -term) %>% 
  ungroup() %>% 
  mutate(passage = as.numeric(flux_date)) %>% 
  mutate(ch4 = estimate,
         rank_ch4 = rank(ch4),
         log_ch4 = log10(ch4 + abs(min(ch4)) + 0.001)) %>% 
  filter(passage != 6) %>% 
  select(-std.error, -statistic, -p.value, -estimate)
```

```{r identify_selected}

# Identify the selected jars in the fluxes dataframe
selected$selected <- TRUE
fluxes <- 
  fluxes %>% 
  left_join(selected, by = c('passage', 'jar')) %>% 
  mutate(selected = !is.na(selected)) %>% 
  select(-jar) %>% 
  select(flux_date, passage, treat, rep, ch4:selected)
```

```{r print_data}
kable(fluxes)
```
